One exact and one random sampling method to assess the reliability of inferences from network enrichment analysis

### 2018-07-31 doc/genesetdp.tex

To test the consistency of the methods, we also investigated the correspondance between the $p$~values reported by GeneSetDP and GeneSetMC. As can be seen in Fig~\ref{fig:pscatter}, the relative difference is larger for lower $p$~values, likely due to the sampling errors of GeneSetMC.

\begin{figure}[htb]
  \begin{center}
		  \begin{tabular}[t]{c}
        FIXME: Make this scatterplot in log-log, GeneSetDP on x-axis, GeneSetMC on y-axis.
        (Idea from reviewer comment in email 2018-06-08.)
%				\includegraphics[width=1.0\textwidth]{FIXME}
		\end{tabular}
  \end{center}
  \caption{{\bf Correspondance between GeneSetDP's and GeneSetMC's $p$~values.} We selected 10000 random sets of 10, 20 and 30 genes from the investigated genome definition and calculated their $p$ values with GeneSetMC and GeneSetDP against the ``Glycolysis/Gluconeogenesis'' pathway. We subsequently plotted the obtained $p$~values against each other .}
  \label{fig:pscatter}
\end{figure}

>>>>

To test the consistency of the methods, we also investigated the correspondance between the $p$~values reported by GeneSetDP and GeneSetMC. As can be seen in Figure~\ref{fig:pscatter}, the results are consistent as expected.

\begin{figure}[htb]
  \begin{center}
		  \begin{tabular}[t]{c}
        % FIXME: Make this scatterplot in log-log, GeneSetDP on x-axis, GeneSetMC on y-axis.
        % (Idea from reviewer comment in email 2018-06-08.)
				\includegraphics[width=1.0\textwidth]{figures/scatter_dp_mc.png}
		\end{tabular}
  \end{center}
  \caption{{\bf Correspondance between GeneSetDP's and GeneSetMC's $p$~values.} We selected 10000 random sets of 10, 20 and 30 genes from the investigated genome definition and calculated their $p$ values with GeneSetMC and GeneSetDP against the ``Glycolysis/Gluconeogenesis'' pathway. We subsequently plotted the obtained $p$~values against each other. Again, the dashed line shows $y = x$ and the dotted lines $y = 2x$ and $y = 0.5x$.}
  \label{fig:pscatter}
\end{figure}
